Cerebral malaria follow-up visit data

### 2021-10-05 cm_follow_up_figures.Rmd
plot all tracings

load("results.Rdata")
load("follow_up_results.Rdata")

@@

# combine visit 1 with follow-ups
df_results_all <- df_results %>% 
  mutate(subject_id = substr(subject_id, start = 1, stop = 6)) %>% 
  left_join(df_fu_results %>% select(-c(number, Status)), by = "subject_id")

# reorganize for plotting
df_results_all_plot <- df_results_all %>% 
  dplyr::select(-visit) %>% 
  dplyr::filter(subject_id %in% df_fu_results$subject_id) %>% 
  pivot_longer(cols = 4:ncol(.), names_to = "variable", values_to = "value") %>% 
  mutate(follow_up = ifelse(grepl("fu", variable), "follow-up", "initial visit")) %>% 
  mutate(follow_up = factor(follow_up, levels = c("initial visit", "follow-up")))

@@

>>>>

load("all_dfa_results.Rdata")

@@

# reorganize for plotting
df_results_all_plot <- df_brain_dfa_results %>% 
  dplyr::filter(!is.na(avg_Hb_conc_fu)) %>% 
  pivot_longer(cols = 3:ncol(.), names_to = "variable", values_to = "value") %>% 
  mutate(follow_up = ifelse(grepl("fu", variable), "follow-up", "initial visit")) %>% 
  mutate(follow_up = factor(follow_up, levels = c("initial visit", "follow-up")))

@@

  # geom_segment(aes(x = 1, y = ycoord, xend = 2, yend = ycoord), size = 0.3) +
  # geom_segment(aes(x = 1, y = ycoord, xend = 1, yend = ycoord - .04*ycoord), size = 0.3) +
  # geom_segment(aes(x = 2, y = ycoord, xend = 2, yend = ycoord - .04*ycoord), size = 0.3) +
  # geom_text(x = 1.5, aes(y = ycoord + .025*ycoord, label = paste0("p = ", pvals))) +
